---
title: "Logo-Sequence Generator for RNA-Immunoprecipitation followed by sequencing"
author:
  affiliation: Interdisciplinary Center for Clinical Research - RWTH-Aachen
  name: Ali T. Abdallah
  fontsize: 15pt
date: "17.06.2021"
output: 
  html_notebook:
  highlight: kate
  theme: yeti
---

<style>
.main-container{
  min-width: 1800px;!important
  margin-left: auto;!important
  margin-right: auto;!important
  font-size: 15px;!important
}
.tabset{
  font-size: 15px;!important
}
.download{
	padding: 10px 15px;
	background: #4479BA;
	color: #FFF;
	-webkit-border-radius: 4px;
	-moz-border-radius: 4px;
	border-radius: 4px;
	border: solid 1px #20538D;
	text-shadow: 0 -1px 0 rgba(0, 0, 0, 0.4);
	-webkit-box-shadow: inset 0 1px 0 rgba(255, 255, 255, 0.4), 0 1px 1px rgba(0, 0, 0, 0.2);
	-moz-box-shadow: inset 0 1px 0 rgba(255, 255, 255, 0.4), 0 1px 1px rgba(0, 0, 0, 0.2);
	box-shadow: inset 0 1px 0 rgba(255, 255, 255, 0.4), 0 1px 1px rgba(0, 0, 0, 0.2);
	-webkit-transition-duration: 0.2s;
	-moz-transition-duration: 0.2s;
	transition-duration: 0.2s;
	-webkit-user-select:none;
	-moz-user-select:none;
	-ms-user-select:none;
	user-select:none;
}
.download:hover{
	background: #356094;
	border: solid 1px #2A4E77;
	text-decoration: none;
}
.download:active{
	-webkit-box-shadow: inset 0 1px 4px rgba(0, 0, 0, 0.6);
	-moz-box-shadow: inset 0 1px 4px rgba(0, 0, 0, 0.6);
	box-shadow: inset 0 1px 4px rgba(0, 0, 0, 0.6);
	background: #2E5481;
	border: solid 1px #203E5F;
}

#toc_container {
    background: #f9f9f9 none repeat scroll 0 0;
    border: 0px solid #aaa;
    display: table;
    font-size: 100%;
    margin-bottom: 1em;
    padding: 10px;
    width: auto;
}

.toc_title {
    font-weight: 700;
    text-align: left;
}

h4 a{
color:#000080;
font-weight:bold;
}

h5 a{
color:#008080;
font-weight:bold;
}

li a {
color:#000080
}

#toc_container li, #toc_container ol, #toc_container ol li{
    list-style: outside none none !important;
}
</style>


<div id="toc_container">
<p class="toc_title" id="back"><h4 style="color:#800000"><b>Table of Contents</b></h4></p>
<ol class="toc_list" style="font-size:15px">
  <li><a href="#top_transcript_table"><b>1. Table of top abundant transcripts (FPKM > 1) </b></a></li>
  <li><a href="#Sequences"><b>2. Sequences and annotation</b></a> </li>
  <li><a href="#Motifs"><b>3. Generation of motif instances</b></a></li>
  <li><a href="#Matches"><b>4. Generation of match data</b></a></li>
  <li><a href="#Logos"><b>5. Generation of sequence Logos</b></a></li>
</ol>
</div>



## {.tabset .tabset-fade }

```{r setup, echo=F}
library(biomaRt)
library(DT)
library(genefilter)
library(tidyverse)
library(ggplot2)
library(ggseqlogo)
library(cowplot)
```
```{r config, echo=F}
DEBUG <- F
LOCAL_MOUNT_POINT  <- "/nextgen"
REMOTE_MOUNT_POINT <- ""
PATH_MOUNT_PREFIX  <- paste(LOCAL_MOUNT_POINT,"/",REMOTE_MOUNT_POINT, sep="")
BATCH_PATHS <- list("scratch/data/projects/devries/tables_200911", "scratch/data/projects/devries/tables_200911") 
SAMPLE_NAME_PREFIX <- "SummarizedMatchTable_GFiltered_"
BATCH.NAMES <- c("mrna", "ncrna")
SAMPLE_BATCHES <- list(c("mrna"), c("ncrna"))
mRNA <- 1
ncRNA <- 2
ColorCombo53 <- c("#028482", "#7ABA7A","#B76EB8") 
genes <- read.table("Genes", header=T, sep = "\t")
genes.old <- read.table("devries_geneList.txt", header=T, sep = "\t")
genes$GENE_SYMBOL
```

<h4 id="top_transcript_table"> <a href="#back">1. Table of top abundant transcripts (FPKM >= 1)</a></h4>
Keep transcripts with predicted FPKM greater or equal to 1 in either of both conditions (hnRNPL vs. InputKG1a)—furthermore, remove transcripts with a non-positive log of FPKM ratio. Here called L2FC. This is possible are not all transcripts in the list of top genes must be upregulated (L2FC >= 1).


```{r echo=F}
sample_ids <- list("1934", "1938", "1942", "1932", "1936", "1940")
names(sample_ids) <- c("IPhnRNPK", "IPhnRNPK_2", "IPhnRNPK_3", "InputKG1a", "InputKG1a_3", "InputKG1a_2")
fpkm_list <- vector("list", length(sample_ids))
for(i in 1:length(sample_ids)){
  fpkm_list[[i]] <- read.table(paste("/nextgen/scratch/nextgen/runs/rnaseq.119/3_cufflinks/",sample_ids[[i]],"/isoforms.fpkm_tracking", sep=""), header=T, sep="\t")
}
for(i in 1:length(sample_ids)){
  fpkm_list[[i]] <-   fpkm_list[[i]][,c("t_name", "gene_id", "gene_name", "FPKM", "cov")]
  colnames(fpkm_list[[i]]) <- c("t_name", "gene_id", "gene_name", paste("FPKM.",names(sample_ids)[i],sep=""), paste("COV.",names(sample_ids)[i],sep=""))
}
library(genefilter)
library(tidyverse)
fpkm_table <- fpkm_list %>% purrr::reduce(left_join, by = c("t_name", "gene_id", "gene_name"))
fpkm_table.filtered <- fpkm_table[(fpkm_table$COV.IPhnRNPK >= 1 & fpkm_table$COV.IPhnRNPK_2 >= 1 & fpkm_table$COV.IPhnRNPK_3 >= 1 & fpkm_table$FPKM.IPhnRNPK >= 1 & fpkm_table$FPKM.IPhnRNPK_2 >= 1 & fpkm_table$FPKM.IPhnRNPK_3 >= 1) ,]

# (fpkm_table$COV.InputKG1a >= 1 & fpkm_table$COV.InputKG1a_2 >= 1 & fpkm_table$COV.InputKG1a_3 >= 1 & fpkm_table$FPKM.InputKG1a >= 1 & fpkm_table$FPKM.InputKG1a_2 >= 1 & fpkm_table$FPKM.InputKG1a_3 >= 1)

fpkm_table.filtered <- fpkm_table.filtered[fpkm_table.filtered$gene_name %in% genes$GENE_SYMBOL | fpkm_table.filtered$gene_id %in% genes$GENE_SYMBOL,]
colnames(fpkm_table.filtered)[1:3] <- c("ensembl_transcript_id", "ensembl_gene_id", "hgnc_symbol")

fpkm_table.filtered <- fpkm_table.filtered[, c(1,2,3,4,6,8,10,12,14,5,7,9,11,13,15)]
fpkm_table.filtered$meanHnRNPK <- rowMeans(fpkm_table.filtered[,4:6])
fpkm_table.filtered$meanInputKG1a <- rowMeans(fpkm_table.filtered[,7:9])
fpkm_table.filtered$stdDevHnRNPM <- rowSds(as.matrix(fpkm_table.filtered[,4:6]))
fpkm_table.filtered$stdDevInputKG1a <- rowSds(as.matrix(fpkm_table.filtered[,7:9]))
fpkm_table.filtered$L2FC <- log2(fpkm_table.filtered$meanHnRNPK/(1+fpkm_table.filtered$meanInputKG1a))
fpkm_table.filtered <- fpkm_table.filtered[fpkm_table.filtered$L2FC >= 1 & fpkm_table.filtered$stdDevHnRNPM < fpkm_table.filtered$meanHnRNPK,]
fpkm_table.filtered <- fpkm_table.filtered[, c(1:3,ncol(fpkm_table.filtered),5:ncol(fpkm_table.filtered)-1)]
DT::datatable(as.data.frame(fpkm_table.filtered), rownames = F, filter = 'top', caption = 'FPKM data of abundant transcripts of top genes', extensions = 'Buttons', options = list(scrollX = TRUE, dom = 'Bfrtip', buttons = list(list(extend='copy',title="FPKMAbundantTopTranscripts"),list(extend='csv',title="FPKMAbundantTopTranscripts"),list(extend='excel',filename="FPKMAbundantTopTranscripts"),list(extend='pdf',filename="FPKMAbundantTopTranscripts"),list(extend='print',filename="FPKMAbundantTopTranscripts")), autoWidth = TRUE, pageLength = 10, columnDefs = list(list(className = 'dt-left'))))
```


## {.tabset .tabset-fade }

<h4 id="Sequences"> <a href="#back">2. Sequences and Annotation</a></h4>

```{r read.database, echo=F}
## Select Ensembl Mart
ensmart <- biomaRt::useMart("ensembl",  host="uswest.ensembl.org", dataset="hsapiens_gene_ensembl", verbose=F) 
## Get all transcript annotations
#listAttributes(ensmart)
top_transcripts_meta <- biomaRt::getBM(attributes=c("hgnc_symbol", 
                                                    "ensembl_gene_id", 
                                                    "chromosome_name", 
                                                    "start_position", 
                                                    "end_position",
                                                    "strand",
                                                    "ensembl_transcript_id",
                                                    "transcript_start",
                                                    "transcript_end",
                                                    "transcript_biotype"), 
                                       filters="hgnc_symbol" , 
                                       values=unique(fpkm_table.filtered$hgnc_symbol), 
                                       mart=ensmart)
three_utr <- 1
five_utr <- 2
cds <- 3
column_names <- c("3utr", "5utr", "coding")
sequence_batches <- vector("list", 3)
filtered.sequence_batches <- vector("list", 3)
top_transcripts_meta <- top_transcripts_meta[top_transcripts_meta$ensembl_transcript_id %in% fpkm_table.filtered$ensembl_transcript_id,]

## Get all transcript sequences.
for(i in 1:length(sequence_batches)){
  sequence_batches[[i]] <- biomaRt::getSequence(id=top_transcripts_meta$ensembl_transcript_id, seqType = column_names[i], mart = ensmart, type="ensembl_transcript_id")
   sequence_batches[[i]][,1] <- gsub(pattern = "T", replacement = "U", x =  sequence_batches[[i]][,1])
  filtered.sequence_batches[[i]] <- sequence_batches[[i]][sequence_batches[[i]][,1] != "Sequence unavailable",]
   filtered.sequence_batches[[i]] <- merge( filtered.sequence_batches[[i]] , top_transcripts_meta, by="ensembl_transcript_id")
}

ncrna <- biomaRt::getSequence(id=top_transcripts_meta$ensembl_transcript_id, seqType ="cdna", mart = ensmart, type="ensembl_transcript_id")
ncrna[,1] <- gsub(pattern = "T", replacement = "U", x =  ncrna[,1])
ncrna <- ncrna[ncrna$ensembl_transcript_id %in% top_transcripts_meta[top_transcripts_meta$transcript_biotype=="lncRNA", ]$ensembl_transcript_id,]
```

### Metadata based on gene id
```{r echo=F}
DT::datatable(as.data.frame(top_transcripts_meta), rownames = F, filter = 'top', caption = 'Metadata of abundant transcripts of top genes with available sequence', extensions = 'Buttons', options = list(scrollX = TRUE, dom = 'Bfrtip', buttons = list(list(extend='copy',title="MetadataAbundantTopTranscripts"),list(extend='csv',title="MetadataAbundantTopTranscripts"),list(extend='excel',filename="MetadataAbundantTopTranscripts"),list(extend='pdf',filename="MetadataAbundantTopTranscripts"),list(extend='print',filename="MetadataAbundantTopTranscripts")), autoWidth = TRUE, pageLength = 10, columnDefs = list(list(className = 'dt-left'))))
```

### Metadata based on available mRNA sequences
```{r echo=F}
DT::datatable(as.data.frame(top_transcripts_meta[top_transcripts_meta$ensembl_transcript_id %in% filtered.sequence_batches[[1]]$ensembl_transcript_id
                                                 | top_transcripts_meta$ensembl_transcript_id %in% filtered.sequence_batches[[2]]$ensembl_transcript_id
                                                 | top_transcripts_meta$ensembl_transcript_id %in% filtered.sequence_batches[[3]]$ensembl_transcript_id,]), rownames = F, filter = 'top', caption = 'Metadata of abundant transcripts of top genes with available sequence', extensions = 'Buttons', options = list(scrollX = TRUE, dom = 'Bfrtip', buttons = list(list(extend='copy',title="MetadataAbundantTopTranscripts"),list(extend='csv',title="MetadataAbundantTopTranscripts"),list(extend='excel',filename="MetadataAbundantTopTranscripts"),list(extend='pdf',filename="MetadataAbundantTopTranscripts"),list(extend='print',filename="MetadataAbundantTopTranscripts")), autoWidth = TRUE, pageLength = 10, columnDefs = list(list(className = 'dt-left'))))
```

### Metadata based on available lncRNA sequences
```{r echo=F}
ncrna.batch <- top_transcripts_meta[top_transcripts_meta$ensembl_transcript_id %in% ncrna$ensembl_transcript_id,]
DT::datatable(as.data.frame(top_transcripts_meta[top_transcripts_meta$ensembl_transcript_id %in% ncrna$ensembl_transcript_id,]), rownames = F, filter = 'top', caption = 'Metadata of abundant transcripts of top genes with available sequence', extensions = 'Buttons', options = list(scrollX = TRUE, dom = 'Bfrtip', buttons = list(list(extend='copy',title="MetadataAbundantTopTranscripts"),list(extend='csv',title="MetadataAbundantTopTranscripts"),list(extend='excel',filename="MetadataAbundantTopTranscripts"),list(extend='pdf',filename="MetadataAbundantTopTranscripts"),list(extend='print',filename="MetadataAbundantTopTranscripts")), autoWidth = TRUE, pageLength = 10, columnDefs = list(list(className = 'dt-left'))))
```


### Summary on available regions in top transcripts

```{r echo=F}
ndf <- vector("list", 4)
region_names <- c("three_utr", "five_utr", "cds", "ncrna") 
for(i in 1:3){
  number_of_sequences <- list(nrow(sequence_batches[[i]]), nrow(filtered.sequence_batches[[i]]))
  names(number_of_sequences) <- c("all_sequences", "available_sequences")
  ndf[[i]] <- as.data.frame(t(as.data.frame(number_of_sequences)))
  colnames(ndf[[i]]) <- c("counts")
  ndf[[i]]$region <- region_names[i]
  ndf[[i]]$type <- ifelse(rownames(ndf[[i]])=="available_sequences", "available", "all")
  ndf[[i]] <- ndf[[i]][, c(2,1,3)]
}

ns <- list(12,12)
names(ns) <- c("all_sequences","available_sequences")
ndf[[4]] <- as.data.frame(t(as.data.frame(ns)))
colnames(ndf[[4]]) <- c("counts")
ndf[[4]]$region <- region_names[4]
ndf[[4]]$type <- ifelse(rownames(ndf[[4]])=="available_sequences", "available", "all")
ndf[[4]] <- ndf[[4]][, c(2,1,3)]

region_availability <- do.call("rbind", ndf)
DT::datatable(as.data.frame(region_availability), rownames = F, filter = 'top', caption = 'Number of available transcript regions', extensions = 'Buttons', options = list(dom = 'Bfrtip', buttons = list(list(extend='copy',title="RegionAvailabilityStats"),list(extend='csv',title="RegionAvailabilityStats"),list(extend='excel',filename="RegionAvailabilityStats"),list(extend='pdf',filename="RegionAvailabilityStats"),list(extend='print',filename="RegionAvailabilityStats")), autoWidth = TRUE, pageLength = 10, columnDefs = list(list(className = 'dt-left'))))



```


## {.tabset .tabset-fade }


<h4 id="Motifs"><a href="#back">3. Generation of Motif Instances</a></h4>

```{r echo=F}
flank10 <- paste(rep(".",10),collapse="")
flank20 <- paste(rep(".",20),collapse="")
# Interaction Motifs
int.motifs <- vector("list", 13)
int.motifs.noGs <- vector("list", 13)
# Regulatory Motifs
reg.motifs <- vector("list", 23)
reg.motifs.noGs <- vector("list", 23)
# Unspecific Tetranucleotide (UCCC or CCCC)
tetra.motif.10 <- paste(flank10,"(UCCC|CCCC)",flank10, sep="")
tetra.motif.20 <- paste(flank20,"(UCCC|CCCC)",flank20, sep="")

# Generate all interaction motif instances.
for(si in 1:12){
  int.motifs[[si]] <- paste(flank10,"(UCCC|CCCC)",paste(rep(".",si-1),collapse=""),"(UCCC|CCCC)",flank10, sep="")
  int.motifs.noGs[[si]] <- paste(flank10,"(UCCC|CCCC)",paste(rep("[ACU]",si-1),collapse=""),"(UCCC|CCCC)",flank10, sep="")
}

# Generate all regulatory motif instances.
for(s in 0:22){
  reg.motifs[[s+1]] <- list()
  for(l in 0:s){
   for(m in 0:max(0,s-l)){
     for(r in 0:max(0,s-(l+m))){
       if(l+m+r==s){
          # print(paste("l:",l," m:",m, " r:",r," = ",s,sep=""))
          reg.motifs[[s+1]][[length(reg.motifs[[s+1]])+1]] <- paste(
                                                            "(..........",
                                                            "(UCCC|CCCC)",
                                                            paste(rep(".",l),collapse=""),
                                                            "(UCCC|CCCC)",
                                                            paste(rep(".",m),collapse=""),
                                                            "(UCCC|CCCC)",
                                                            paste(rep(".",r),collapse=""),
                                                            "(UCCC|CCCC)",
                                                            "..........)", 
                                                            sep="")
       }
     }
   }
  }
  reg.motifs[[s+1]] <- paste(unique(unlist( reg.motifs[[s+1]])),collapse=" | ")
}

# Generate all regulatory motif instances.
for(s in 0:22){
  reg.motifs.noGs[[s+1]] <- list()
  for(l in 0:s){
   for(m in 0:max(0,s-l)){
     for(r in 0:max(0,s-(l+m))){
       if(l+m+r==s){
          # print(paste("l:",l," m:",m, " r:",r," = ",s,sep=""))
          reg.motifs.noGs[[s+1]][[length(reg.motifs.noGs[[s+1]])+1]] <- paste(
                                                            "(..........",
                                                            "(UCCC|CCCC)",
                                                            paste(rep("[ACU]",l),collapse=""),
                                                            "(UCCC|CCCC)",
                                                            paste(rep("[ACU]",m),collapse=""),
                                                            "(UCCC|CCCC)",
                                                            paste(rep("[ACU]",r),collapse=""),
                                                            "(UCCC|CCCC)",
                                                            "..........)", 
                                                            sep="")
       }
     }
   }
  }
  reg.motifs.noGs[[s+1]] <- paste(unique(unlist( reg.motifs.noGs[[s+1]])),collapse=" | ")
}

```


### Interaction Motifs
```{r table.int.motifs, echo=F}
df.int.motifs <- data.frame(`motif instance`=NULL, `motif length`=NULL)

for(s in 0:11){
  tmp_df <- as.data.frame(int.motifs[[s+1]])
  tmp_df$length <- s+8
  colnames(tmp_df) <- c("motif instance", "motif length")
  #tmp_df <- tmp_df[,c(2,1)]
  df.int.motifs <- rbind(df.int.motifs, tmp_df)
}
DT::datatable(as.data.frame(df.int.motifs), rownames = F, filter = 'top', caption = 'Table of all interaction motifs by length', extensions = 'Buttons', options = list(dom = 'Bfrtip', buttons = list(list(extend='copy',title="IntMotifsListByLength"),list(extend='csv',title="IntMotifsListByLength"),list(extend='excel',filename="IntMotifsListByLength"),list(extend='pdf',filename="IntMotifsListByLength"),list(extend='print',filename="IntMotifsListByLength")), autoWidth = TRUE, pageLength = 10, columnDefs = list(list(className = 'dt-left'))))

```

### Interaction Motifs (no critical Gs)
```{r table.int.motifs.noGs, echo=F}
df.int.motifs.noGs <- data.frame(`motif instance`=NULL, `motif length`=NULL)

for(s in 0:11){
  tmp_df <- as.data.frame(int.motifs.noGs[[s+1]])
  tmp_df$length <- s+8
  colnames(tmp_df) <- c("motif instance", "motif length")
  #tmp_df <- tmp_df[,c(2,1)]
  df.int.motifs.noGs <- rbind(df.int.motifs.noGs, tmp_df)
}
DT::datatable(as.data.frame(df.int.motifs.noGs), rownames = F, filter = 'top', caption = 'Table of all interaction motifs without critical Gs by length', extensions = 'Buttons', options = list(dom = 'Bfrtip', buttons = list(list(extend='copy',title="IntMotifsListByLength"),list(extend='csv',title="IntMotifsListByLength"),list(extend='excel',filename="IntMotifsListByLength"),list(extend='pdf',filename="IntMotifsListByLength"),list(extend='print',filename="IntMotifsListByLength")), autoWidth = TRUE, pageLength = 10, columnDefs = list(list(className = 'dt-left'))))

```

### Regulatory Motifs
```{r table.reg.motifs, echo=F}
df <- data.frame(`motif instance`=NULL, `motif length`=NULL)

for(s in 0:22){
  tmp_df <- as.data.frame(reg.motifs[[s+1]])
  tmp_df$length <- s+16
  colnames(tmp_df) <- c("motif instance", "motif length")
  #tmp_df <- tmp_df[,c(2,1)]
  df <- rbind(df, tmp_df)
}


DT::datatable(as.data.frame(df), rownames = F, filter = 'top', caption = 'Table of all regulatory motifs by length', extensions = 'Buttons', options = list(scrollX = TRUE, dom = 'Bfrtip', buttons = list(list(extend='copy',title="RegMotifsListByLength"),list(extend='csv',title="RegMotifsListByLength"),list(extend='excel',filename="RegMotifsListByLength"),list(extend='pdf',filename="RegMotifsListByLength"),list(extend='print',filename="RegMotifsListByLength")), autoWidth = TRUE, pageLength = 5, columnDefs = list(list(className = 'dt-left'))))

```


## {.tabset .tabset-fade }

<h4 id="Matches"><a href="#back">4. Generation of Match Data</a></h4>
```{r read.ncrna.input, echo=F}
## Split into ncrna and mrna
## Split into 3utr, 5utr and cds
## Split into interaction and regulatory motifs
ncrna <- 1
mrna <- 2
interaction <- 1
regulatory <- 2
three_utr <- 1
five_utr <- 2
cds <- 3

## biotypes
match_data <- vector("list", 2)
match_data[[ncrna]] <- vector("list", 3)
match_data[[mrna]] <- vector("list", 3)

for(sb in 1:length(sequence_batches)){
  match_data[[mrna]][[sb]] <- filtered.sequence_batches[[sb]][filtered.sequence_batches[[sb]]$transcript_biotype=="protein_coding",]
}

for(sb in 1:length(sequence_batches)){
  match_data[[ncrna]][[sb]] <- filtered.sequence_batches[[sb]][ncrna.batch$transcript_biotype=="lncRNA",]
}

```


```{r generate.matches.mrna, echo=F}
specific.matches.mrna <- vector("list", 3)
specific.regulatory.matches.mrna <- vector("list", 3)
unspecific.matches.mrna <- vector("list", 3)
column_names <- c("3utr", "5utr", "coding")
for(sb in 1:3){
  print(paste("Computing matches for ",column_names[sb]," region.", sep=""))
  specific.matches.mrna[[sb]] <- vector("list", 11)
  for(s in 1:12){
    print(paste("    Computing matches for interaction motif of length ",(s+7),".", sep=""))
    specific.matches.mrna[[sb]][[s]] <- match_data[[mrna]][[sb]][,2] %>% 
                                        stringr::str_extract_all(int.motifs[[s]], simplify = F) %>% 
                                        na.omit() %>% 
                                        unlist() %>% 
                                        as.vector()
    print(paste("    Computing matches for interaction motif of length ",(s+7)," ended.", sep=""))
  }
  unspecific.matches.mrna[[sb]] <- as.vector(na.omit(unlist(stringr::str_extract_all(match_data[[mrna]][[sb]][,2], tetra.motif.10))))
  print(paste("Computing matches for unspecific tetranucleotide CCCC or UCCCC ended.", sep=""))
}
```


```{r generate.matches.mrna.noGs, echo=F}
specific.matches.mrna.noGs <- vector("list", 3)
specific.regulatory.matches.mrna.noGs <- vector("list", 3)
unspecific.matches.mrna.noGs <- vector("list", 3)
column_names <- c("3utr", "5utr", "coding")
for(sb in 1:3){
  print(paste("Computing matches for ",column_names[sb]," region.", sep=""))
  specific.matches.mrna.noGs[[sb]] <- vector("list", 11)
  for(s in 1:12){
    print(paste("    Computing matches for interaction motif of length ",(s+7),".", sep=""))
    specific.matches.mrna.noGs[[sb]][[s]] <- match_data[[mrna]][[sb]][,2] %>% 
                                        stringr::str_extract_all(int.motifs.noGs[[s]], simplify = F) %>% 
                                        na.omit() %>% 
                                        unlist() %>% 
                                        as.vector()
    print(paste("    Computing matches for interaction motif of length ",(s+7)," ended.", sep=""))
  }
  unspecific.matches.mrna.noGs[[sb]] <- as.vector(na.omit(unlist(stringr::str_extract_all(match_data[[mrna]][[sb]][,2], tetra.motif.10))))
  print(paste("Computing matches for unspecific tetranucleotide CCCC or UCCCC ended.", sep=""))
}
```


### 3-UTR
```{r echo=F}
matches.mrna.3.utr <- as.data.frame(unlist(specific.matches.mrna[[three_utr]]))
colnames(matches.mrna.3.utr) <- "matches.mrna.3.utr"
matches.mrna.3.utr

#DT::datatable(as.data.frame(matches.mrna.3.utr), rownames = F, filter = 'top', caption = 'Table of all regulatory motifs by length', extensions = 'Buttons', options = list(scrollX = TRUE, dom = 'Bfrtip', buttons = list(list(extend='copy',title="RegMotifsListByLength"),list(extend='csv',title="RegMotifsListByLength"),list(extend='excel',filename="RegMotifsListByLength"),list(extend='pdf',filename="RegMotifsListByLength"),list(extend='print',filename="RegMotifsListByLength")), autoWidth = TRUE, pageLength = 5, columnDefs = list(list(className = 'dt-left'))))


```

### 3-UTR (no critical Gs)
```{r echo=F}
matches.mrna.noGs.3.utr <- as.data.frame(unlist(specific.matches.mrna.noGs[[three_utr]]))
colnames(matches.mrna.noGs.3.utr) <- "matches.mrna.noGs.3.utr"
matches.mrna.noGs.3.utr

#DT::datatable(as.data.frame(matches.mrna.noGs.3.utr), rownames = F, filter = 'top', caption = 'Table of all regulatory motifs by length', extensions = 'Buttons', options = list(scrollX = TRUE, dom = 'Bfrtip', buttons = list(list(extend='copy',title="RegMotifsListByLength"),list(extend='csv',title="RegMotifsListByLength"),list(extend='excel',filename="RegMotifsListByLength"),list(extend='pdf',filename="RegMotifsListByLength"),list(extend='print',filename="RegMotifsListByLength")), autoWidth = TRUE, pageLength = 5, columnDefs = list(list(className = 'dt-left'))))


```

### 5-UTR
```{r echo=F}
matches.mrna.5.utr <- as.data.frame(unlist(specific.matches.mrna[[five_utr]]))
colnames(matches.mrna.5.utr) <- "matches.mrna.5.utr"
matches.mrna.5.utr
```

### 5-UTR (no critical Gs)
```{r echo=F}
matches.mrna.noGs.5.utr <- as.data.frame(unlist(specific.matches.mrna.noGs[[five_utr]]))
colnames(matches.mrna.noGs.5.utr) <- "matches.mrna.noGs.5.utr"
matches.mrna.noGs.5.utr
```

### CDS
```{r echo=F}
matches.mrna.cds <- as.data.frame(unlist(specific.matches.mrna[[cds]]))
colnames(matches.mrna.cds) <- "matches.mrna.cds"
matches.mrna.cds
```

### CDS (no critical Gs)
```{r echo=F}
matches.mrna.noGs.cds <- as.data.frame(unlist(specific.matches.mrna.noGs[[cds]]))
colnames(matches.mrna.noGs.cds) <- "matches.mrna.noGs.cds"
matches.mrna.noGs.cds
```


```{r generat.matches.ncrna, echo=F}
print(paste("Computing matches for ",column_names[sb]," region.", sep=""))
specific.matches.ncrna <- vector("list", 11)
for(s in 1:12){
    print(paste("    Computing matches for interaction motif of length ",(s+7),".", sep=""))
    specific.matches.ncrna[[s]] <- match_data[[ncrna]][[sb]][,2] %>% 
                                        stringr::str_extract_all(int.motifs[[s]], simplify = F) %>% 
                                        na.omit() %>% 
                                        unlist() %>% 
                                        as.vector()
    print(paste("    Computing matches for interaction motif of length ",(s+7)," ended.", sep=""))
  }
  unspecific.matches.ncrna <- as.vector(na.omit(unlist(stringr::str_extract_all(match_data[[ncrna]][[sb]][,2], tetra.motif.10))))
  print(paste("Computing matches for unspecific tetranucleotide CCCC or UCCCC ended.", sep=""))
```

```{r generat.matches.ncrna.noGs, echo=F}
print(paste("Computing matches for ",column_names[sb]," region.", sep=""))
specific.matches.ncrna.noGs <- vector("list", 11)
for(s in 1:11){
    print(paste("    Computing matches for interaction motif of length ",(s+7),".", sep=""))
    specific.matches.ncrna.noGs[[s]] <- match_data[[ncrna]][[sb]][,2] %>% 
                                        stringr::str_extract_all(int.motifs.noGs[[s]], simplify = F) %>% 
                                        na.omit() %>% 
                                        unlist() %>% 
                                        as.vector()
    print(paste("    Computing matches for interaction motif of length ",(s+7)," ended.", sep=""))
  }
  unspecific.matches.ncrna.noGs <- as.vector(na.omit(unlist(stringr::str_extract_all(match_data[[ncrna]][[sb]][,2], tetra.motif.10))))
  print(paste("Computing matches for unspecific tetranucleotide CCCC or UCCCC ended.", sep=""))
```
### lncRNA
```{r echo=F}
matches.ncrna <- as.data.frame(unlist(specific.matches.ncrna))
colnames(matches.ncrna) <- "matches.mrna.ncrna"
matches.ncrna
```
### lncRNA (no critical Gs)
```{r echo=F}
matches.ncrna.noGs <- as.data.frame(unlist(specific.matches.ncrna.noGs))
colnames(matches.ncrna.noGs) <- "matches.mrna.ncrna.noGs"
matches.ncrna.noGs
```

```{r echo=F}
all.specific.matches.mrna <- vector("list", 12)
all.specific.matches.mrna.noGs <- vector("list", 12)
all.unspecific.matches.mrna <- vector("list", 12)
all.unspecific.matches.mrna.noGs  <- vector("list", 12)
for(l in 1:12){
  all.specific.matches.mrna.noGs[[l]] <- c(specific.matches.mrna.noGs[[three_utr]][[l]], specific.matches.mrna.noGs[[five_utr]][[l]], specific.matches.mrna.noGs[[cds]][[l]])
  all.specific.matches.mrna[[l]] <- c(specific.matches.mrna[[three_utr]][[l]], specific.matches.mrna[[five_utr]][[l]], specific.matches.mrna[[cds]][[l]])
}
all.unspecific.matches.mrna <- c(unspecific.matches.mrna[[three_utr]], unspecific.matches.mrna[[five_utr]], unspecific.matches.mrna[[cds]])
all.unspecific.matches.mrna.noGs <- c(unspecific.matches.mrna.noGs[[three_utr]], unspecific.matches.mrna.noGs[[five_utr]], unspecific.matches.mrna.noGs[[cds]])
```

## {.tabset .tabset-fade }

<h4 id="Logos"><a href="#back">5. Generation of Sequence Logos</a></h4>

<h5 id="LogosInteraction"><a href="#back">5.1 Interaction</a></h4>
### All (Summary)
```{r logo.for.specific.tetra.all, fig.width=15, fig.height=5,  echo=F}
GENERATE_PDF <- F
method="bits"

ncol=1
method="bits"
sepcific.mrna.list <- (c(all.specific.matches.mrna))
unspecfic.mrna.list <- list(all.unspecific.matches.mrna)
sub.mrna.left <- unlist(sepcific.mrna.list)
sub.mrna.left <- substring(sub.mrna.left, first = 1, last=14)
sub.mrna.right <- unlist(sepcific.mrna.list)
sub.mrna.right <- substring(sub.mrna.right, first = nchar(sub.mrna.right)-13, last=nchar(sub.mrna.right))
sub.mrna.unspecific <- all.unspecific.matches.mrna


sub.mrna.left <- list(sub.mrna.left)
names(sub.mrna.left) <- "Motif Upstream"
sub.mrna.right <- list(sub.mrna.right)
names(sub.mrna.right) <- "Motif Downstream"
sub.mrna.unspecific <- list(sub.mrna.unspecific)
names(sub.mrna.unspecific) <- "Unspecific Tetranucleotide (UCCC or CCCC) Up- and Downstream"

ggsl.mrna.left <- ggseqlogo(sub.mrna.left, ncol = ncol, method=method)
ggsl.mrna.right <- ggseqlogo(sub.mrna.right, ncol = ncol, method=method)
ggsl.mrna.unspecific <- ggseqlogo(sub.mrna.unspecific, ncol = ncol, method=method)

ncol=1
sepcific.mrna.noGs.list <- (c(all.specific.matches.mrna.noGs))
unspecfic.mrna.noGs.list <- list(all.unspecific.matches.mrna.noGs)
sub.mrna.noGs.left <- unlist(sepcific.mrna.noGs.list)
sub.mrna.noGs.left <- substring(sub.mrna.noGs.left, first = 1, last=14)
sub.mrna.noGs.right <- unlist(sepcific.mrna.noGs.list)
sub.mrna.noGs.right <- substring(sub.mrna.noGs.right, first = nchar(sub.mrna.noGs.right)-13, last=nchar(sub.mrna.noGs.right))
sub.mrna.unspecific <- all.unspecific.matches.mrna


sub.mrna.noGs.left <- list(sub.mrna.noGs.left)
names(sub.mrna.noGs.left) <- "Motif Upstream"
sub.mrna.noGs.right <- list(sub.mrna.noGs.right)
names(sub.mrna.noGs.right) <- "Motif Downstream"
sub.mrna.noGs.unspecific <- list(sub.mrna.unspecific)
names(sub.mrna.noGs.unspecific) <- "Unspecific Tetranucleotide (UCCC or CCCC) Up- and Downstream"

ggsl.mrna.noGs.left <- ggseqlogo(sub.mrna.noGs.left, ncol = ncol, method=method)
ggsl.mrna.noGs.right <- ggseqlogo(sub.mrna.noGs.right, ncol = ncol, method=method)
ggsl.mrna.noGs.unspecific <- ggseqlogo(sub.mrna.unspecific, ncol = ncol, method=method)

criticalPlotTitle <- ggplot()+ggtitle("With critical Gs")+theme_void()+theme(plot.title = element_text(hjust = 0.5, colour = "darkred"))
nonCriticalPlotTitle <- ggplot()+ggtitle("Without critical Gs")+theme_void()+theme(plot.title = element_text(hjust = 0.5, colour = "darkred"))

criticalMotifPlot <- plot_grid(ggsl.mrna.left, ggsl.mrna.right,ncol=2)
criticalUnspecTetraPlot <- plot_grid(ggsl.mrna.unspecific)
nonCriticalMotifPlot <- plot_grid(ggsl.mrna.noGs.left, ggsl.mrna.noGs.right,ncol=2)
nonCriticalUnspecificTetraPlot <- plot_grid(ggsl.mrna.noGs.unspecific)

plot_grid(plot_grid(plot_grid(criticalPlotTitle, criticalMotifPlot, rel_heights = c(1,10), ncol=1), criticalUnspecTetraPlot, ncol=1),
          plot_grid(plot_grid(nonCriticalPlotTitle, nonCriticalMotifPlot, rel_heights = c(1,10), ncol=1), nonCriticalUnspecificTetraPlot, ncol=1), ncol=2)


if(GENERATE_PDF){
  pdf("Paper/Data/All_Summary.pdf", width=15, height=5)
  plot_grid(plot_grid(plot_grid(criticalPlotTitle, criticalMotifPlot, rel_heights = c(1,10), ncol=1), criticalUnspecTetraPlot, ncol=1),
            plot_grid(plot_grid(nonCriticalPlotTitle, nonCriticalMotifPlot, rel_heights = c(1,10), ncol=1), nonCriticalUnspecificTetraPlot, ncol=1), ncol=2)
  
  dev.off()
}
```

### All (Detailed)
```{r fig.height=20, fig.width=16, echo=F}
library(ggseqlogo)
library(cowplot)
lengths.noGs <- vector("list", 12)
for(l in 1:12){
 lengths.noGs[[l]] <- length(all.specific.matches.mrna.noGs[[l]])
}

lengths <- vector("list", 12)
for(l in 1:12){
 lengths[[l]] <- length(all.specific.matches.mrna[[l]])
}

ldf.noGs <- as.data.frame(unlist(lengths.noGs))
colnames(ldf.noGs) <- "frequency"
ldf.noGs$Type <- "Without critical G's"
ldf.noGs$SUM <- sum(ldf.noGs$frequency)
ldf <- as.data.frame(unlist(lengths))
colnames(ldf) <- "frequency"
ldf$Type <- "With critical G's"
ldf$SUM <- sum(ldf$frequency)
ldf$perc <- round(100*ldf$frequency/ldf$SUM, 2)
ldf.noGs$perc <- round(100*ldf.noGs$frequency/ldf.noGs$SUM, 2)
list.mrna.noGs <- c(all.specific.matches.mrna.noGs, list(all.unspecific.matches.mrna.noGs))
list.mrna <- c(all.specific.matches.mrna, list(all.unspecific.matches.mrna))
names(list.mrna.noGs) <- c(paste("Length ",8:19," - Frequency: ", ldf.noGs$perc,"%", sep=""), "Unspecific Tetranucleotide (UCCC or CCCC)")
names(list.mrna) <- c(paste("Length ",8:19," - Frequency: ", ldf$perc,"%", sep=""), "Unspecific Tetranucleotide (UCCC or CCCC)")
method="bit"
ggsl.mrna.noGs <- ggseqlogo(list.mrna.noGs, ncol = ncol, method=method)
ggsl.mrna <- ggseqlogo(list.mrna, ncol = ncol, method=method)

plot_grid(plot_grid(criticalPlotTitle, nonCriticalPlotTitle, ncol=2), plot_grid(ggsl.mrna, ggsl.mrna.noGs, ncol=2), rel_heights = c(0.1,10), ncol=1)

if(GENERATE_PDF){
  pdf("Paper/Data/All_detailed.pdf", width=16, height=20)
  plot_grid(plot_grid(criticalPlotTitle, nonCriticalPlotTitle, ncol=2), plot_grid(ggsl.mrna, ggsl.mrna.noGs, ncol=2), rel_heights = c(0.1,10), ncol=1)
  dev.off()
}
```

### 3-UTR (Summary)
```{r logo.for.specific.tetra.3.utr, fig.width=10, fig.height=10, echo=F}
require(ggplot2)
require(ggseqlogo)
ncol=1
method="bits"
sepcific.mrna.list <- (c(specific.matches.mrna[[three_utr]]))
unspecfic.mrna.list <- list(unspecific.matches.mrna[[three_utr]])
sub.mrna.left <- unlist(sepcific.mrna.list)
sub.mrna.left <- substring(sub.mrna.left, first = 1, last=14)
sub.mrna.right <- unlist(sepcific.mrna.list)
sub.mrna.right <- substring(sub.mrna.right, first = nchar(sub.mrna.right)-13, last=nchar(sub.mrna.right))
sub.mrna.unspecific <- unspecific.matches.mrna[[three_utr]]


sub.mrna.left <- list(sub.mrna.left)
names(sub.mrna.left) <- "Motif Upstream"
sub.mrna.right <- list(sub.mrna.right)
names(sub.mrna.right) <- "Motif Downstream"
sub.mrna.unspecific <- list(sub.mrna.unspecific)
names(sub.mrna.unspecific) <- "Unspecific Tetranucleotide (UCCC or CCCC) Up- and Downstream"

ggsl.mrna.left <- ggseqlogo(sub.mrna.left, ncol = ncol, method=method)
ggsl.mrna.right <- ggseqlogo(sub.mrna.right, ncol = ncol, method=method)
ggsl.mrna.unspecific <- ggseqlogo(sub.mrna.unspecific, ncol = ncol, method=method)

```

```{r logo.for.specific.tetra.3.utr.noGs, fig.width=15, fig.height=5, echo=F}
require(ggplot2)
require(ggseqlogo)
library(cowplot)
ncol=1
method="bits"
sepcific.mrna.noGs.list <- (c(specific.matches.mrna.noGs[[three_utr]]))
unspecfic.mrna.noGs.list <- list(unspecific.matches.mrna.noGs[[three_utr]])
sub.mrna.noGs.left <- unlist(sepcific.mrna.noGs.list)
sub.mrna.noGs.left <- substring(sub.mrna.noGs.left, first = 1, last=14)
sub.mrna.noGs.right <- unlist(sepcific.mrna.noGs.list)
sub.mrna.noGs.right <- substring(sub.mrna.noGs.right, first = nchar(sub.mrna.noGs.right)-13, last=nchar(sub.mrna.noGs.right))
sub.mrna.unspecific <- unspecific.matches.mrna[[three_utr]]


sub.mrna.noGs.left <- list(sub.mrna.noGs.left)
names(sub.mrna.noGs.left) <- "Motif Upstream"
sub.mrna.noGs.right <- list(sub.mrna.noGs.right)
names(sub.mrna.noGs.right) <- "Motif Downstream"
sub.mrna.noGs.unspecific <- list(sub.mrna.unspecific)
names(sub.mrna.noGs.unspecific) <- "Unspecific Tetranucleotide (UCCC or CCCC) Up- and Downstream"

ggsl.mrna.noGs.left <- ggseqlogo(sub.mrna.noGs.left, ncol = ncol, method=method)
ggsl.mrna.noGs.right <- ggseqlogo(sub.mrna.noGs.right, ncol = ncol, method=method)
ggsl.mrna.noGs.unspecific <- ggseqlogo(sub.mrna.unspecific, ncol = ncol, method=method)

criticalPlotTitle <- ggplot()+ggtitle("With critical Gs")+theme_void()+theme(plot.title = element_text(hjust = 0.5, colour = "darkred"))
nonCriticalPlotTitle <- ggplot()+ggtitle("Without critical Gs")+theme_void()+theme(plot.title = element_text(hjust = 0.5, colour = "darkred"))

criticalMotifPlot <- plot_grid(ggsl.mrna.left, ggsl.mrna.right,ncol=2)
criticalUnspecTetraPlot <- plot_grid(ggsl.mrna.unspecific)
nonCriticalMotifPlot <- plot_grid(ggsl.mrna.noGs.left, ggsl.mrna.noGs.right,ncol=2)
nonCriticalUnspecificTetraPlot <- plot_grid(ggsl.mrna.noGs.unspecific)

plot_grid(plot_grid(plot_grid(criticalPlotTitle, criticalMotifPlot, rel_heights = c(1,10), ncol=1), criticalUnspecTetraPlot, ncol=1),
          plot_grid(plot_grid(nonCriticalPlotTitle, nonCriticalMotifPlot, rel_heights = c(1,10), ncol=1), nonCriticalUnspecificTetraPlot, ncol=1), ncol=2)


if(GENERATE_PDF){
  pdf("Paper/Data/3UTR_Summary.pdf", width=15, height=5)
  plot_grid(plot_grid(plot_grid(criticalPlotTitle, criticalMotifPlot, rel_heights = c(1,10), ncol=1), criticalUnspecTetraPlot, ncol=1),
            plot_grid(plot_grid(nonCriticalPlotTitle, nonCriticalMotifPlot, rel_heights = c(1,10), ncol=1), nonCriticalUnspecificTetraPlot, ncol=1), ncol=2)
  dev.off()
}

```

### 3-UTR (Detailed)
```{r fig.height=20, fig.width=16, echo=F}
library(ggseqlogo)
library(cowplot)
lengths.noGs <- vector("list", 12)
for(l in 1:12){
 lengths.noGs[[l]] <- length(specific.matches.mrna.noGs[[three_utr]][[l]])
}

lengths <- vector("list", 12)
for(l in 1:12){
 lengths[[l]] <- length(specific.matches.mrna[[three_utr]][[l]])
}

ldf.noGs <- as.data.frame(unlist(lengths.noGs))
colnames(ldf.noGs) <- "frequency"
ldf.noGs$Type <- "Without critical G's"
ldf.noGs$SUM <- sum(ldf.noGs$frequency)
ldf <- as.data.frame(unlist(lengths))
colnames(ldf) <- "frequency"
ldf$Type <- "With critical G's"
ldf$SUM <- sum(ldf$frequency)
ldf$perc <- round(100*ldf$frequency/ldf$SUM, 2)
ldf.noGs$perc <- round(100*ldf.noGs$frequency/ldf.noGs$SUM, 2)



list.mrna.noGs <- c(specific.matches.mrna.noGs[[three_utr]], list(unspecific.matches.mrna.noGs[[three_utr]]))
list.mrna <- c(specific.matches.mrna[[three_utr]], list(unspecific.matches.mrna[[three_utr]]))

names(list.mrna.noGs) <- c(paste("Length ",8:19," - Frequency: ", ldf.noGs$perc,"%", sep=""), "Unspecific Tetranucleotide (UCCC or CCCC)")
names(list.mrna) <- c(paste("Length ",8:19," - Frequency: ", ldf$perc,"%", sep=""), "Unspecific Tetranucleotide (UCCC or CCCC)")
method="bit"
ggsl.mrna.noGs <- ggseqlogo(list.mrna.noGs, ncol = ncol, method=method)
ggsl.mrna <- ggseqlogo(list.mrna, ncol = ncol, method=method)

plot_grid(plot_grid(criticalPlotTitle, nonCriticalPlotTitle, ncol=2), plot_grid(ggsl.mrna, ggsl.mrna.noGs, ncol=2), rel_heights = c(0.1,10), ncol=1)


if(GENERATE_PDF){
  pdf("Paper/Data/3UTR_detailed.pdf", width=16, height=20)
  plot_grid(plot_grid(criticalPlotTitle, nonCriticalPlotTitle, ncol=2), plot_grid(ggsl.mrna, ggsl.mrna.noGs, ncol=2), rel_heights = c(0.1,10), ncol=1)
  dev.off()
}

```


### 5-UTR (Summary)

```{r logo.for.specific.tetra.5.utr, fig.width=15, fig.height=5, echo=F}
require(ggplot2)
require(ggseqlogo)

### Detailed version
ggsl.mrna <- ggseqlogo( c(specific.matches.mrna[[five_utr]], list(unspecific.matches.mrna[[five_utr]])), ncol = ncol, method=method)

### With critical Gs
ncol=1
method="bits"
sepcific.mrna.five_utr.list <- (c(specific.matches.mrna[[five_utr]]))
sub.mrna.five_utr.left <- unlist(sepcific.mrna.five_utr.list)
sub.mrna.five_utr.left <- substring(sub.mrna.five_utr.left, first = 1, last=14)
sub.mrna.five_utr.right <- unlist(sepcific.mrna.five_utr.list)
sub.mrna.five_utr.right <- substring(sub.mrna.five_utr.right, first = nchar(sub.mrna.five_utr.right)-13, last=nchar(sub.mrna.five_utr.right))
sub.mrna.five_utr.unspecific <-  unspecific.matches.mrna[[five_utr]]

sub.mrna.five_utr.left <- list(sub.mrna.five_utr.left)
names(sub.mrna.five_utr.left) <- "Motif Upstream"
sub.mrna.five_utr.right <- list(sub.mrna.five_utr.right)
names(sub.mrna.five_utr.right) <- "Motif Downstream"
sub.mrna.five_utr.unspecific <- list(sub.mrna.five_utr.unspecific)
names(sub.mrna.five_utr.unspecific) <- "Unspecific Tetranucleotide (UCCC or CCCC) Up- and Downstream"

### Create plots
ggsl.mrna.five_utr.left <- ggseqlogo(sub.mrna.five_utr.left, ncol = ncol, method=method)
ggsl.mrna.five_utr.right <- ggseqlogo(sub.mrna.five_utr.right, ncol = ncol, method=method)
ggsl.mrna.five_utr.unspecific <- ggseqlogo(sub.mrna.five_utr.unspecific, ncol = ncol, method=method)

### Without critical Gs
sepcific.mrna.noGs.five_utr.list <- (c(specific.matches.mrna.noGs[[five_utr]]))
sub.mrna.noGs.five_utr.left <- unlist(sepcific.mrna.noGs.five_utr.list)
sub.mrna.noGs.five_utr.left <- substring(sub.mrna.noGs.five_utr.left, first = 1, last=14)
sub.mrna.noGs.five_utr.right <- unlist(sepcific.mrna.noGs.five_utr.list)
sub.mrna.noGs.five_utr.right <- substring(sub.mrna.noGs.five_utr.right, first = nchar(sub.mrna.noGs.five_utr.right)-13, last=nchar(sub.mrna.noGs.five_utr.right))
sub.mrna.noGs.five_utr.unspecific <-  unspecific.matches.mrna.noGs[[five_utr]]

sub.mrna.noGs.five_utr.left <- list(sub.mrna.noGs.five_utr.left)
names(sub.mrna.noGs.five_utr.left) <- "Motif Upstream"
sub.mrna.noGs.five_utr.right <- list(sub.mrna.noGs.five_utr.right)
names(sub.mrna.noGs.five_utr.right) <- "Motif Downstream"
sub.mrna.noGs.five_utr.unspecific <- list(sub.mrna.noGs.five_utr.unspecific)
names(sub.mrna.noGs.five_utr.unspecific) <- "Unspecific Tetranucleotide (UCCC or CCCC) Up- and Downstream"

### Create plots
ggsl.mrna.noGs.five_utr.left <- ggseqlogo(sub.mrna.noGs.five_utr.left, ncol = ncol, method=method)
ggsl.mrna.noGs.five_utr.right <- ggseqlogo(sub.mrna.noGs.five_utr.right, ncol = ncol, method=method)
ggsl.mrna.noGs.five_utr.unspecific <- ggseqlogo(sub.mrna.noGs.five_utr.unspecific, ncol = ncol, method=method)

### Shot plots grid.
library(cowplot)
criticalMotifPlot <- plot_grid(ggsl.mrna.five_utr.left, ggsl.mrna.five_utr.right,ncol=2)
criticalUnspecTetraPlot <- plot_grid(ggsl.mrna.five_utr.unspecific)
nonCriticalMotifPlot <- plot_grid(ggsl.mrna.noGs.five_utr.left, ggsl.mrna.noGs.five_utr.right,ncol=2)
nonCriticalUnspecificTetraPlot <- plot_grid(ggsl.mrna.noGs.five_utr.unspecific)

plot_grid(plot_grid(plot_grid(criticalPlotTitle, criticalMotifPlot, rel_heights = c(1,10), ncol=1), criticalUnspecTetraPlot, ncol=1),
          plot_grid(plot_grid(nonCriticalPlotTitle, nonCriticalMotifPlot, rel_heights = c(1,10), ncol=1), nonCriticalUnspecificTetraPlot, ncol=1), ncol=2)


if(GENERATE_PDF){
  pdf("Paper/Data/5UTR_Summary.pdf", width=15, height=5)
  plot_grid(plot_grid(plot_grid(criticalPlotTitle, criticalMotifPlot, rel_heights = c(1,10), ncol=1), criticalUnspecTetraPlot, ncol=1),
            plot_grid(plot_grid(nonCriticalPlotTitle, nonCriticalMotifPlot, rel_heights = c(1,10), ncol=1), nonCriticalUnspecificTetraPlot, ncol=1), ncol=2)
  dev.off()
}
```

### 5-UTR (Detailed)
```{r fig.height=20, fig.width=16, echo=F}
library(ggseqlogo)
library(cowplot)
lengths.noGs <- vector("list", 12)
for(l in 1:12){
 lengths.noGs[[l]] <- length(specific.matches.mrna.noGs[[five_utr]][[l]])
}

lengths <- vector("list", 12)
for(l in 1:12){
 lengths[[l]] <- length(specific.matches.mrna[[five_utr]][[l]])
}

ldf.noGs <- as.data.frame(unlist(lengths.noGs))
colnames(ldf.noGs) <- "frequency"
ldf.noGs$Type <- "Without critical G's"
ldf.noGs$SUM <- sum(ldf.noGs$frequency)
ldf <- as.data.frame(unlist(lengths))
colnames(ldf) <- "frequency"
ldf$Type <- "With critical G's"
ldf$SUM <- sum(ldf$frequency)
ldf$perc <- round(100*ldf$frequency/ldf$SUM, 2)
ldf.noGs$perc <- round(100*ldf.noGs$frequency/ldf.noGs$SUM, 2)
list.mrna.noGs <- c(specific.matches.mrna.noGs[[five_utr]], list(unspecific.matches.mrna.noGs[[five_utr]]))
list.mrna <- c(specific.matches.mrna[[five_utr]], list(unspecific.matches.mrna[[five_utr]]))
names(list.mrna.noGs) <- c(paste("Length ",8:19," - Frequency: ", ldf.noGs$perc,"%", sep=""), "Unspecific Tetranucleotide (UCCC or CCCC)")
names(list.mrna) <- c(paste("Length ",8:19," - Frequency: ", ldf$perc,"%", sep=""), "Unspecific Tetranucleotide (UCCC or CCCC)")
method="bit"
ggsl.mrna.noGs <- ggseqlogo(list.mrna.noGs, ncol = ncol, method=method)
ggsl.mrna <- ggseqlogo(list.mrna, ncol = ncol, method=method)

plot_grid(plot_grid(criticalPlotTitle, nonCriticalPlotTitle, ncol=2), plot_grid(ggsl.mrna, ggsl.mrna.noGs, ncol=2), rel_heights = c(0.1,10), ncol=1)

if(GENERATE_PDF){
  pdf("Paper/Data/5UTR_detailed.pdf", width=16, height=20)
  plot_grid(plot_grid(criticalPlotTitle, nonCriticalPlotTitle, ncol=2), plot_grid(ggsl.mrna, ggsl.mrna.noGs, ncol=2), rel_heights = c(0.1,10), ncol=1)
  dev.off()
}
```



### CDS (Summary)
```{r logo.for.specific.tetra.cds, fig.width=15, fig.height=5, echo=F}
require(ggplot2)
require(ggseqlogo)
ncol=1
method="bit"

### With critical Gs
sepcific.mrna.cds.list <- (c(specific.matches.mrna[[cds]]))
sub.mrna.cds.left <- unlist(sepcific.mrna.cds.list)
sub.mrna.cds.left <- substring(sub.mrna.cds.left, first = 1, last=14)
sub.mrna.cds.right <- unlist(sepcific.mrna.cds.list)
sub.mrna.cds.right <- substring(sub.mrna.cds.right, first = nchar(sub.mrna.cds.right)-13, last=nchar(sub.mrna.cds.right))
sub.mrna.cds.unspecific <-  unspecific.matches.mrna[[cds]]

sub.mrna.cds.left <- list(sub.mrna.cds.left)
names(sub.mrna.cds.left) <- "Motif Upstream"
sub.mrna.cds.right <- list(sub.mrna.cds.right)
names(sub.mrna.cds.right) <- "Motif Downstream"
sub.mrna.cds.unspecific <- list(sub.mrna.cds.unspecific)
names(sub.mrna.cds.unspecific) <- "Unspecific Tetranucleotide (UCCC or CCCC) Up- and Downstream"

ggsl.mrna.cds.left <- ggseqlogo(sub.mrna.cds.left, ncol = ncol, method=method)
ggsl.mrna.cds.right <- ggseqlogo(sub.mrna.cds.right, ncol = ncol, method=method)
ggsl.mrna.cds.unspecific <- ggseqlogo(sub.mrna.cds.unspecific, ncol = ncol, method=method)

### Without critical G's
sepcific.mrna.noGs.cds.list <- (c(specific.matches.mrna.noGs[[cds]]))
sub.mrna.noGs.cds.left <- unlist(sepcific.mrna.noGs.cds.list)
sub.mrna.noGs.cds.left <- substring(sub.mrna.noGs.cds.left, first = 1, last=14)
sub.mrna.noGs.cds.right <- unlist(sepcific.mrna.noGs.cds.list)
sub.mrna.noGs.cds.right <- substring(sub.mrna.noGs.cds.right, first = nchar(sub.mrna.noGs.cds.right)-13, last=nchar(sub.mrna.noGs.cds.right))
sub.mrna.noGs.cds.unspecific <-  unspecific.matches.mrna.noGs[[cds]]

sub.mrna.noGs.cds.left <- list(sub.mrna.noGs.cds.left)
names(sub.mrna.noGs.cds.left) <- "Motif Upstream"
sub.mrna.noGs.cds.right <- list(sub.mrna.noGs.cds.right)
names(sub.mrna.noGs.cds.right) <- "Motif Downstream"
sub.mrna.noGs.cds.unspecific <- list(sub.mrna.noGs.cds.unspecific)
names(sub.mrna.noGs.cds.unspecific) <- "Unspecific Tetranucleotide (UCCC or CCCC) Up- and Downstream"

ggsl.mrna.noGs.cds.left <- ggseqlogo(sub.mrna.noGs.cds.left, ncol = ncol, method=method)
ggsl.mrna.noGs.cds.right <- ggseqlogo(sub.mrna.noGs.cds.right, ncol = ncol, method=method)
ggsl.mrna.noGs.cds.unspecific <- ggseqlogo(sub.mrna.noGs.cds.unspecific, ncol = ncol, method=method)

criticalMotifPlot <- plot_grid(ggsl.mrna.cds.left, ggsl.mrna.cds.right,ncol=2)
criticalUnspecTetraPlot <- plot_grid(ggsl.mrna.cds.unspecific)
nonCriticalMotifPlot <- plot_grid(ggsl.mrna.noGs.cds.left, ggsl.mrna.noGs.cds.right,ncol=2)
nonCriticalUnspecificTetraPlot <- plot_grid(ggsl.mrna.noGs.cds.unspecific)


library(cowplot)
plot_grid(plot_grid(plot_grid(criticalPlotTitle, criticalMotifPlot, rel_heights = c(1,10), ncol=1), criticalUnspecTetraPlot, ncol=1),
          plot_grid(plot_grid(nonCriticalPlotTitle, nonCriticalMotifPlot, rel_heights = c(1,10), ncol=1), nonCriticalUnspecificTetraPlot, ncol=1), ncol=2)


if(GENERATE_PDF){
  pdf("Paper/Data/CDS_Summary.pdf", width=15, height=5)
  plot_grid(plot_grid(plot_grid(criticalPlotTitle, criticalMotifPlot, rel_heights = c(1,10), ncol=1), criticalUnspecTetraPlot, ncol=1),
            plot_grid(plot_grid(nonCriticalPlotTitle, nonCriticalMotifPlot, rel_heights = c(1,10), ncol=1), nonCriticalUnspecificTetraPlot, ncol=1), ncol=2)
  dev.off()
}

```

### CDS (Detailed)
```{r fig.height=20, fig.width=16, echo=F}

lengths.noGs <- vector("list", 12)
for(l in 1:12){
 lengths.noGs[[l]] <- length(specific.matches.mrna.noGs[[cds]][[l]])
}

lengths <- vector("list", 12)
for(l in 1:12){
 lengths[[l]] <- length(specific.matches.mrna[[cds]][[l]])
}

ldf.noGs <- as.data.frame(unlist(lengths.noGs))
colnames(ldf.noGs) <- "frequency"
ldf.noGs$Type <- "Without critical G's"
ldf.noGs$SUM <- sum(ldf.noGs$frequency)
ldf <- as.data.frame(unlist(lengths))
colnames(ldf) <- "frequency"
ldf$Type <- "With critical G's"
ldf$SUM <- sum(ldf$frequency)
ldf$perc <- round(100*ldf$frequency/ldf$SUM, 2)
ldf.noGs$perc <- round(100*ldf.noGs$frequency/ldf.noGs$SUM, 2)



list.mrna.noGs <- c(specific.matches.mrna.noGs[[cds]], list(unspecific.matches.mrna.noGs[[cds]]))
list.mrna <- c(specific.matches.mrna[[cds]], list(unspecific.matches.mrna[[cds]]))

names(list.mrna.noGs) <- c(paste("Length ",8:19," - Frequency: ", ldf.noGs$perc,"%", sep=""), "Unspecific Tetranucleotide (UCCC or CCCC)")
names(list.mrna) <- c(paste("Length ",8:19," - Frequency: ", ldf$perc,"%", sep=""), "Unspecific Tetranucleotide (UCCC or CCCC)")

ggsl.mrna.noGs <- ggseqlogo(list.mrna.noGs, ncol = ncol, method=method)
ggsl.mrna <- ggseqlogo(list.mrna, ncol = ncol, method=method)

plot_grid(plot_grid(criticalPlotTitle, nonCriticalPlotTitle, ncol=2), plot_grid(ggsl.mrna, ggsl.mrna.noGs, ncol=2), rel_heights = c(0.1,10), ncol=1)
  

if(GENERATE_PDF){
  pdf("Paper/Data/CDS_detailed.pdf", width=16, height=20)
  plot_grid(plot_grid(criticalPlotTitle, nonCriticalPlotTitle, ncol=2), plot_grid(ggsl.mrna, ggsl.mrna.noGs, ncol=2), rel_heights = c(0.1,10), ncol=1)
  dev.off()
}
```


### Non Coding RNA (Summary)

```{r logo.for.specific.tetra.ncrna, fig.width=15, fig.height=5, echo=F}
require(ggplot2)
require(ggseqlogo)
ggsl.ncrna <- ggseqlogo( c(specific.matches.ncrna, list(unspecific.matches.ncrna)), ncol = ncol, method=method)


sepcific.mrna.ncrna.list <- (c(specific.matches.mrna[[ncrna]]))
sub.mrna.ncrna.left <- unlist(sepcific.mrna.ncrna.list)
sub.mrna.ncrna.left <- substring(sub.mrna.ncrna.left, first = 1, last=14)
sub.mrna.ncrna.right <- unlist(sepcific.mrna.ncrna.list)
sub.mrna.ncrna.right <- substring(sub.mrna.ncrna.right, first = nchar(sub.mrna.ncrna.right)-13, last=nchar(sub.mrna.ncrna.right))
sub.mrna.ncrna.unspecific <-  unspecific.matches.mrna[[ncrna]]

sub.mrna.ncrna.left <- list(sub.mrna.ncrna.left)
names(sub.mrna.ncrna.left) <- "Motif Upstream"
sub.mrna.ncrna.right <- list(sub.mrna.ncrna.right)
names(sub.mrna.ncrna.right) <- "Motif Downstream"
sub.mrna.ncrna.unspecific <- list(sub.mrna.ncrna.unspecific)
names(sub.mrna.ncrna.unspecific) <- "Unspecific Tetranucleotide (UCCC or CCCC) Up- and Downstream"

ggsl.mrna.ncrna.left <- ggseqlogo(sub.mrna.ncrna.left, ncol = ncol, method=method)
ggsl.mrna.ncrna.right <- ggseqlogo(sub.mrna.ncrna.right, ncol = ncol, method=method)
ggsl.mrna.ncrna.unspecific <- ggseqlogo(sub.mrna.ncrna.unspecific, ncol = ncol, method=method)

```


```{r logo.for.specific.tetra.ncrna.noGs, fig.width=15, fig.height=5, echo=F}
require(ggplot2)
require(ggseqlogo)
ggsl.ncrna <- ggseqlogo( c(specific.matches.ncrna, list(unspecific.matches.ncrna)), ncol = ncol, method=method)

sepcific.mrna.ncrna.noGs.list <- (c(specific.matches.mrna.noGs[[ncrna]]))
sub.mrna.ncrna.noGs.left <- unlist(sepcific.mrna.ncrna.noGs.list)
sub.mrna.ncrna.noGs.left <- substring(sub.mrna.ncrna.noGs.left, first = 1, last=14)
sub.mrna.ncrna.noGs.right <- unlist(sepcific.mrna.ncrna.noGs.list)
sub.mrna.ncrna.noGs.right <- substring(sub.mrna.ncrna.noGs.right, first = nchar(sub.mrna.ncrna.noGs.right)-13, last=nchar(sub.mrna.ncrna.noGs.right))
sub.mrna.ncrna.noGs.unspecific <-  unspecific.matches.mrna[[ncrna]]

sub.mrna.ncrna.noGs.left <- list(sub.mrna.ncrna.noGs.left)
names(sub.mrna.ncrna.noGs.left) <- "Motif Upstream"
sub.mrna.ncrna.noGs.right <- list(sub.mrna.ncrna.noGs.right)
names(sub.mrna.ncrna.noGs.right) <- "Motif Downstream"
sub.mrna.ncrna.noGs.unspecific <- list(sub.mrna.ncrna.noGs.unspecific)
names(sub.mrna.ncrna.noGs.unspecific) <- "Unspecific Tetranucleotide (UCCC or CCCC) Up- and Downstream"

ggsl.mrna.ncrna.noGs.left <- ggseqlogo(sub.mrna.ncrna.noGs.left, ncol = ncol, method=method)
ggsl.mrna.ncrna.noGs.right <- ggseqlogo(sub.mrna.ncrna.noGs.right, ncol = ncol, method=method)
ggsl.mrna.ncrna.noGs.unspecific <- ggseqlogo(sub.mrna.ncrna.noGs.unspecific, ncol = ncol, method=method)

library(cowplot)
plot_grid(plot_grid(plot_grid(criticalPlotTitle, plot_grid(ggsl.mrna.ncrna.left, ggsl.mrna.ncrna.right,ncol=2), rel_heights = c(1,10), ncol=1), ggsl.mrna.ncrna.unspecific, ncol=1),
          plot_grid(plot_grid(nonCriticalPlotTitle, plot_grid(ggsl.mrna.ncrna.noGs.left, ggsl.mrna.ncrna.noGs.right,ncol=2), rel_heights = c(1,10), ncol=1), ggsl.mrna.ncrna.noGs.unspecific, ncol=1), ncol=2)

if(GENERATE_PDF){
pdf("Paper/Data/ncrna_Summary.pdf", width=15, height=5)
library(cowplot)
plot_grid(plot_grid(plot_grid(criticalPlotTitle, plot_grid(ggsl.mrna.ncrna.left, ggsl.mrna.ncrna.right,ncol=2), rel_heights = c(1,10), ncol=1), ggsl.mrna.ncrna.unspecific, ncol=1),
          plot_grid(plot_grid(nonCriticalPlotTitle, plot_grid(ggsl.mrna.ncrna.noGs.left, ggsl.mrna.ncrna.noGs.right,ncol=2), rel_heights = c(1,10), ncol=1), ggsl.mrna.ncrna.noGs.unspecific, ncol=1), ncol=2)
dev.off()
}

```


### Non Coding RNA (Detailed)
```{r fig.height=20, fig.width=16, echo=F}

lengths.noGs <- vector("list", 12)
for(l in 1:12){
 lengths.noGs[[l]] <- length(specific.matches.mrna.noGs[[ncrna]][[l]])
}

lengths <- vector("list", 12)
for(l in 1:12){
 lengths[[l]] <- length(specific.matches.mrna[[ncrna]][[l]])
}

ldf.noGs <- as.data.frame(unlist(lengths.noGs))
colnames(ldf.noGs) <- "frequency"
ldf.noGs$Type <- "Without critical G's"
ldf.noGs$SUM <- sum(ldf.noGs$frequency)
ldf <- as.data.frame(unlist(lengths))
colnames(ldf) <- "frequency"
ldf$Type <- "With critical G's"
ldf$SUM <- sum(ldf$frequency)
ldf$perc <- round(100*ldf$frequency/ldf$SUM, 2)
ldf.noGs$perc <- round(100*ldf.noGs$frequency/ldf.noGs$SUM, 2)



list.mrna.noGs <- c(specific.matches.mrna.noGs[[ncrna]], list(unspecific.matches.mrna.noGs[[ncrna]]))
list.mrna <- c(specific.matches.mrna[[ncrna]], list(unspecific.matches.mrna[[ncrna]]))

names(list.mrna.noGs) <- c(paste("Length ",8:19," - Frequency: ", ldf.noGs$perc,"%", sep=""), "Unspecific Tetranucleotide (UCCC or CCCC)")
names(list.mrna) <- c(paste("Length ",8:19," - Frequency: ", ldf$perc,"%", sep=""), "Unspecific Tetranucleotide (UCCC or CCCC)")

ggsl.mrna.noGs <- ggseqlogo(list.mrna.noGs, ncol = ncol, method=method)
ggsl.mrna <- ggseqlogo(list.mrna, ncol = ncol, method=method)

                                                                                                                    
plot_grid(plot_grid(criticalPlotTitle, nonCriticalPlotTitle, ncol=2), plot_grid(ggsl.mrna, ggsl.mrna.noGs, ncol=2), rel_heights = c(0.1,10), ncol=1)


if(GENERATE_PDF){
  pdf("Paper/Data/ncrna_detailed.pdf", width=16, height=20)
  plot_grid(plot_grid(criticalPlotTitle, nonCriticalPlotTitle, ncol=2), plot_grid(ggsl.mrna, ggsl.mrna.noGs, ncol=2), rel_heights = c(0.1,10), ncol=1)
  dev.off()
}
```

## {.tabset .tabset-fade }

### Session Info
```{r echo=F}
sessionInfo()
```





